---
title: "Monthly Data Imports"
author: "E. Mendonsa"
date: "2026-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r message=FALSE}

library(tidyverse)
library(data.table)
library(readr)
library(readxl)
library(purrr)

siteName <- "Arnold"

monthlyData_path <- "C:/Users/emendons/OneDrive - California Department of Water Resources/Water Quality Lab - DWR - Fish Restoration Program/Data Downloads/Arnold" 

```


Step 1: Import monthly datasets and Combine into a List. 
```{r}

#Run R script: Step1_CreateList_MonthlyData

source("scripts/Step1_CreateList_MonthlyData.R")


```


Step 2: Clip each monthly dataframe within list. This removes times when the sonde is out of water during deployment/retrieval 
```{r}

#Run R script: Step2_DataClipping.R

source("scripts/Step2_DataClipping.R")

```


Step 3: Create a site-specific single dataframe, combining all clipped monthly datasets
```{r}

#Run R script: Step3_CombineData.R

source("scripts/Step3_CombineData.R")

##Use as double check when needed. Should match "combined_rawData_rbind" ##
#combined_rawData_fulljoin <- data_list %>% 
#  reduce(full_join)

#Save list as .RDS file and Excel file
write_rds(filtered_list, file = paste("siteData/",siteName,"_list_monthlyDataclipped.rds",sep=""))

```


Step 4: Format Dataframe (rename columns, combine duplicate columns, remove extra columns, etc)
```{r}

#Run R script: Step4_FormatDataframe.R

source("scripts/Step4_FormatDataframe.R")


```



Step 5: Save Rdata and Excel: Clipped and Formatted Dataframe
```{r}

#Save RDS for Clipped/Formatted Dataframe
write_rds(SiteData_filtered, file = paste("siteData/",siteName,"_dataframe_monthlyDataclipped.rds",sep=""))

#Save CSV for Clipped/Formatted Dataframe
write.csv(SiteData_filtered, file = paste("siteData/",siteName,"_dataframe_monthlyDataclipped.csv",sep=""),row.names = FALSE)

```

